\myTitle

### 2024-01-08 GSI_and_Fst.Rmd
Lots more refinement and additions

```{r input_bypass, include=NEG_USING_SMK, eval=NEG_USING_SMK}
# inputs:
input_list <- list(
  final_baseline = "data/cali-chinook-baseline.rds",
  pop_labels = "inputs/reference-collection-names.csv",
  map_notations = "inputs/map-notations.tsv",
  lfar_base = "data/metagenos_hap2col_lfar.csv"
)
# outputs:
output_list <- list(
  assig_table = "results/GSI_and_Fst/assignment-table-full-baseline.pdf",
  fst_table = "results/GSI_and_Fst/full-baseline-but-no-lfar-Fst-table.pdf",
  assig_table_lfar_all = "results/GSI_and_Fst/assignment-table-full-baseline-plus-lfar.pdf",
  assig_table_lfar_no_miss = "results/GSI_and_Fst/assignment-table-full-baseline-plus-lfar-and-everyone-has-the-lfar.pdf",
  tex_table = "tex/inputs/samples-table.tex",
  gsi_fst_fig = "results/GSI_and_Fst/gsi_and_fst_fig.pdf",
  gsi_fst_fig_crop = "results/GSI_and_Fst/gsi_and_fst_fig-crop.pdf",
  gsi_fst_fig_tex = "tex/images/gsi_and_fst_fig-crop.pdf"
)
# you can create the necessary output directories like this:
dump <- lapply(output_list, function(x)
  dir.create(dirname(x), recursive = TRUE, showWarnings = FALSE)
)
```

@@

```{r}
gsi_fst_fig_for_paper <- plot_grid(
  TAF2$full_plot,
  plot_grid(
    get_legend(TAF2$for_external_legend),
    get_legend(TAF2$for_internal_legend),
    nrow = 1
  ),
  TAF_FST$full_plot,
  nrow = 3,
  rel_heights = c(7,3,7)
)

# and then save that
ggsave(gsi_fst_fig_for_paper, file = output_list$gsi_fst_fig, width = 7, height = 17)

@@

file.rename(from = output_list$gsi_fst_fig, to = output_list$gsi_fst_fig_tex)
```
# Add the LFAR markers to that

Anthony compiled the LFAR markers for the baseline fish.  Not every fish in the baseline
was typed at the LFAR markers.  So, let us see which ones that includes.
```{r}
lfar <- read_csv(input_list$lfar_base)
```

As we saw previously, the loci that we are interested in here are:
```
"NC_037130.1:1062935-1063235",
"NC_037130.1:828619-828919",
"NC_037130.1:864908-865208"
```

However, the 828619 gobbles up reads that don't all map to the right place and
turns out not to be super informative, so we will drop it.

Also, we can call these things as SNPs, not microhaps, which we will do.  The Canonical
Variation file in the snakemake workflow tells us which position is the target SNP in each:

```{r}
focal_loci <- c(
  "NC_037130.1:1062935-1063235",  # target SNP is the second one (position 151 in the amplicon)
  "NC_037130.1:864908-865208"     # target SNP is the first one (position 151 in the amplicon)
)

# so we can pick those out:
lfar_focal <- lfar[,c("Sample_ID", paste(rep(focal_loci, each = 2), c("_1", "_2"), sep = ""))]

# then we will pick out just the target SNPs, too
lfar_focal[, 2] <- str_sub(lfar_focal[[2]], 2, 2)
lfar_focal[, 3] <- str_sub(lfar_focal[[3]], 2, 2)
lfar_focal[, 4] <- str_sub(lfar_focal[[4]], 1, 1)
lfar_focal[, 5] <- str_sub(lfar_focal[[5]], 1, 1)
```

We will left join this onto the baseline by the NMFS_DNA_ID:
```{r}
full_base_lfar <- full_base2 %>%
  left_join(lfar_focal, by = join_by(indiv == Sample_ID))
```

Quickly, let's count up how many individuals we have typed at all these loci.
```{r}
lfar_check <- full_base_lfar[, c("indiv", "repunit", "collection", paste(focal_loci, 1, sep = "_"))] %>%
  mutate(Baseline = "Baseline") %>%
  pivot_longer(-(indiv:collection), names_to = "set") %>%
  mutate(HasData = !is.na(value))

lfar_check %>%
  group_by(repunit, collection, set) %>%
  summarise(
    num_fish_with_genos = sum(HasData)
  ) %>%
  pivot_wider(names_from = set, values_from = num_fish_with_genos)

```
OK! That is great.  We have genotyped pretty much everyone at these LFAR markers except for about 50 of the
FRHS and 10 of the MDF.  If need be would could toss fish that don't have genotypes at any LFAR markers
when we make the assignment table.  Let's get a tibble of baseline individuals telling us whether or not
they have data for at least one of the LFAR markers:
```{r}
at_least_one_lfar <- lfar_check %>%
  filter(set != "Baseline") %>%
  group_by(indiv) %>%
  summarise(at_least_one_lfar = any(HasData == TRUE))

# just see how many there are in total
at_least_one_lfar %>%
  count(at_least_one_lfar)
```
OK! We will compute the assignment table with and without those 66.

## Self-assignment

```{r}
sa_lfar_all <- self_assign(full_base_lfar, gen_start_col = 5)

top_ass_lf <- sa_lfar_all %>%
  group_by(indiv, collection, repunit, inferred_repunit) %>%
  mutate(repu_sclike = sum(scaled_likelihood)) %>%
  group_by(indiv) %>%
  filter(repu_sclike == max(repu_sclike)) %>%
  arrange(indiv, desc(scaled_likelihood)) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(coll_f = factor(collection, levels = collection_order))
```

## Checking for individuals sampled into the wrong collections

We investigate the ones that are in the wrong repunit, and look at their
scaled_repu_likelihoods, to the others.
```{r}
source("R/colors.R")
ta_corr_lf <- top_ass_lf %>%
  filter(repunit == inferred_repunit)
ta_wrong_lf <- top_ass_lf %>%
  filter(repunit != inferred_repunit) %>%
  arrange(collection, repu_sclike) %>%
  group_by(collection) %>%
  mutate(y = 190 + (70/9) * 1:n())

ggplot() +
  geom_histogram(
    data = ta_corr_lf, 
    mapping = aes(x = repu_sclike, fill = inferred_repunit)
  ) +
  geom_point(
    data = ta_wrong_lf,
    mapping = aes(x = repu_sclike, y = y, fill = inferred_repunit),
    size = 3, 
    shape = 21
  ) +
  facet_wrap(~coll_f, ncol = 3) +
  scale_fill_manual(values = gen_bkgrnd_colors)
```
This is much like it was before, however one CHLF fish that was inferred as a spring
run is now inferred as a CHLF.

We toss those 6 that are assigned quite strongly (> 0.98) to a repunit
that they were not sampled in. (Again, the winter-run are clearly true winter
run sampled in the fall or spring collections, and the same is probably true
for MDS-collected fish that are really fall run. We could follow the latter
up with the rosa markers.)

```{r}
ta_lf_filt <- top_ass_lf %>%
  filter(!(repunit != inferred_repunit & repu_sclike > 0.98))

# get the total fraction of assigned vs misassigned fish
ta_lf_filt %>%
  mutate(correct = repunit == inferred_repunit) %>%
  count(correct) %>%
  mutate(fract = n / sum(n))
```
Pretty good.

But, what we really want to see if the table for the collections, to see if we can distinguish
late-fall from fall run any better.

## Assignment table with all the fish

```{r}
# get the function
source("R/taf-prep.R")
source("R/table-as-figure.R")

X2 <- ta_lf_filt %>%
  mutate(
    collection_f = factor(collection, levels = collection_order),
    inferred_coll_f = factor(inferred_collection, levels = collection_order)
  ) %>%
  count(collection_f, inferred_coll_f, .drop = FALSE) %>%
  taf_prep()

# get the result
TAF2_lf <- table_as_figure(
  X = X2, 
  RC_groups = RC_groups,
  external_colors = run_time_colors,
  internal_colors = gen_bkgrnd_colors, 
  plot_margins = c(1, 0.1, 0.7, 0.1)
)

# and plot it
g <- plot_grid(
  TAF2_lf$full_plot,
  plot_grid(
    get_legend(TAF2_lf$for_external_legend),
    get_legend(TAF2_lf$for_internal_legend),
    nrow = 1
  ),
  nrow = 2,
  rel_heights = c(7,3)
)

```{r}
ggsave(g, filename = output_list$assig_table_lfar_all, width = 6, height = 8)
```

## Assignment table with only the fish that have at least one-non-missing genotype among the 3 LFAR genotypes.

We can just filter out fish that don't have a non-missing genotype amongst the three LFARs and call it good.

```{r}
X2_alolf <- ta_lf_filt %>%
  semi_join(at_least_one_lfar %>% filter(at_least_one_lfar), by = join_by(indiv)) %>%
  mutate(
    collection_f = factor(collection, levels = collection_order),
    inferred_coll_f = factor(inferred_collection, levels = collection_order)
  ) %>%
  count(collection_f, inferred_coll_f, .drop = FALSE) %>%
  taf_prep()

# get the result
TAF2_alolf <- table_as_figure(
  X = X2_alolf, 
  RC_groups = RC_groups,
  external_colors = run_time_colors,
  internal_colors = gen_bkgrnd_colors, 
  plot_margins = c(1, 0.1, 0.7, 0.1)
)

# and plot it
g <- plot_grid(
  TAF2_alolf$full_plot,
  plot_grid(
    get_legend(TAF2_alolf$for_external_legend),
    get_legend(TAF2_alolf$for_internal_legend),
    nrow = 1
  ),
  nrow = 2,
  rel_heights = c(7,3)
)

```{r}
ggsave(g, filename = output_list$assig_table_lfar_no_miss, width = 6, height = 8)
```

OK, that is good to see.  The missassignments to or from CHLF are *not* because
they don't have data at the LFAR.  So, we can just use the full data set.

>>>>

```{r input_bypass, include=NEG_USING_SMK, eval=NEG_USING_SMK}
# inputs:
input_list <- list(
  final_baseline = "data/cali-chinook-baseline.rds",
  pop_labels = "inputs/reference-collection-names.csv",
  map_notations = "inputs/map-notations.tsv"
)
# outputs:
output_list <- list(
  assig_table = "results/GSI_and_Fst/assignment-table-full-baseline.pdf",
  fst_table = "results/GSI_and_Fst/full-baseline-but-no-lfar-Fst-table.pdf",
  assig_table_lfar_all = "results/GSI_and_Fst/assignment-table-full-baseline-plus-lfar.pdf",
  assig_table_lfar_no_miss = "results/GSI_and_Fst/assignment-table-full-baseline-plus-lfar-and-everyone-has-the-lfar.pdf",
  tex_table = "tex/inputs/samples-table.tex",
  gsi_fst_fig = "results/GSI_and_Fst/gsi_and_fst_fig.pdf",
  gsi_fst_fig_crop = "results/GSI_and_Fst/gsi_and_fst_fig-crop.pdf",
  gsi_fst_fig_tex = "tex/images/gsi_and_fst_fig-crop.pdf"
)
# you can create the necessary output directories like this:
dump <- lapply(output_list, function(x)
  dir.create(dirname(x), recursive = TRUE, showWarnings = FALSE)
)
```

@@

```{r}
gsi_fst_fig_for_paper <- plot_grid(
  TAF2$full_plot,
  plot_grid(
    get_legend(TAF2$for_external_legend),
    get_legend(TAF2$for_internal_legend),
    nrow = 1
  ),
  TAF_FST$full_plot,
  nrow = 3,
  rel_heights = c(6,1.5,6)
)

# and then save that
ggsave(gsi_fst_fig_for_paper, file = output_list$gsi_fst_fig, width = 7, height = 14)

@@

file.rename(from = output_list$gsi_fst_fig, to = output_list$gsi_fst_fig_tex)
```

### 2024-01-08 tex/body-text-of-paper.tex
Lots more refinement and additions

Here, we present a reference baseline for Chinook salmon, targeted to the complex population 
structure within the Central Valley of California. Chinook salmon of the two main river basins---the 
Sacramento and the San Joaquin---within the Central Valley exhibit the greatest run-timing diversity
within the species.  With four recognized ecotypes, delineated primarily on the basis of run timing
(Fall-, Late-Fall-, Winter-, and Spring-run), adult Chinook salmon can be found migrating or residing
in freshwater every month of the year in California. NEED MORE HERE.

@@

We sampled fish for the reference baselines from 7 locations on the across the two
main tributaries (the Sacramento River and the San Joaquin River) within
California's Central Valley. The baseline also includes samples collected from
one location in the Klamath River, and three rivers of the California coast
Fig.~\ref{fig:map}
%%%%%%%%%%%%%
\begin{figure}
\newcommand{\mapcap}{\footnotesize  A map of sampling locations represented in the reference 
baseline.  The colored circles aside
each location name represent the different run-timing groups of Chinook salmon
included in the collections from the location.  Color codes are as follows: \Wball~=~Winter run,
\LFball{}~=~Late-fall run, \Fball~=~Fall run, \Sball~=~Spring run. Abbreviations used in location names as folows: R. = River; Ck. = Creek; H. = Hatchery; NFH = National Fish Hatchery.}
\begin{center}
\includegraphics[width=\columnwidth]{images/map-crop.pdf}
\end{center}
\caption[\mapcap]{\mapcap}
\label{fig:map}
\end{figure}
%%%%%%%%%%%%%%%

We are going to stick a table in here:
%%%%%%%%%%%%%%%%
\begin{table*}
\caption{Collections of fish in the reference baseline.  The Sampling Months column shows
a pictorial representation of the proportion of each collection sampled in each month.  Colors in
this column correspond to run-timing groups as described in the caption of Figure~\protect\ref{fig:map}.}
{\small 
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} lllllrcr}
\hline\hline\vspace*{0.4ex}
\input{inputs/samples-table.tex}
\end{tabular*}
}
\rule{3cm}{0.3pt}

@@

We will say that we took the SNPs from Clemento et al. and made amplicon based
assays of them

Then we must describe the process by which we got more microhaps.

Then we can talk about assays for the subRoSA markers.

Finally we mention that we have a whole section dedicated to finding the LFAR markers.

\subsection*{Identifying and Designing markers from the Late-Fall Associated Region}

\subsection*{Genetic Variation}

@@

\begin{figure}
\newcommand{\examplecap}{\footnotesize Self-assignment rates  ({\bf a)} and pairwise 
$F_\mathrm{ST}$ values ({\bf b)} for the collections in the baseline.  The codes of the populations
appear on the outer margins of the table atop cells colored according to the run-timing group
of the collection.  Interior cells in which the column and row correspond to the same reporting
unit are colored according to the reporting unit.  For self-assignment tallies, the row corresponds
to the true source collection and the column corresponds to the assigned collection. For $F_\mathrm{ST}$ values, the upper triangle was computed using the baseline microhaplotype
data and the lower triangle was calculated with the whole genome sequence data (where available) from \citet{thompson2020complex}}
\begin{center}
\includegraphics[width=\columnwidth]{images/gsi_and_fst_fig-crop.pdf}
\end{center}
\caption[\examplecap]{\examplecap}
\label{fig:example}
\end{figure}

>>>>

Here, we present a reference baseline for Chinook salmon, targeted to the complex population 
structure within the Central Valley of California. Chinook salmon of the two main river basins---the 
Sacramento and the San Joaquin---within the Central Valley exhibit the greatest run-timing diversity
within the species.  With four recognized ecotypes, delineated primarily on the basis of run timing
(fall-, late-fall-, winter-, and spring-run), adult Chinook salmon can be found migrating or residing
in freshwater every month of the year in California. NEED MORE HERE.

@@

We sampled fish for the reference baselines from XX locations across California.
These locations included sites in the two
main tributaries (the Sacramento River and the San Joaquin River) within
California's Central Valley, the Klamath-Trinity basin in Northern California, and
YY rivers of the California coast
(Fig.~\ref{fig:map}).
%%%%%%%%%%%%%
\begin{figure}
\newcommand{\mapcap}{\footnotesize  A map of sampling locations represented in the reference 
baseline.  The colored circles aside
each location name represent the different run-timing groups of Chinook salmon
included in the collections from the location.  Color codes are as follows: \Wball~=~Winter run,
\LFball{}~=~Late-fall run, \Fball~=~Fall run, \Sball~=~Spring run. Abbreviations used in location names as folows: R. = River; Ck. = Creek; H. = Hatchery; NFH = National Fish Hatchery.}
\begin{center}
\includegraphics[width=\columnwidth]{images/map-crop.pdf}
\end{center}
\caption[\mapcap]{\mapcap}
\label{fig:map}
\end{figure}
%%%%%%%%%%%%%%%
Collections in each location were separate into fish from the different run-timing ecotypes according
to a variety of criteria.  (We need to talk about how these were split into spring run, fall-run, winter 
run, etc.
In total, the samples in the baseline represent fish from five different Evolutionarily Significant 
Units (ESUs) of Chinook salmon \citep{waples1991pacific} A summary of the different collections 
%%%%%%%%%%%%%%%%
\begin{table*}
\caption{\footnotesize Collections of fish in the reference baseline.  The Sampling Months column shows
a pictorial representation of the proportion of each collection sampled in each month.  Colors in
this column correspond to run-timing groups as described in the caption of Fig.~\protect\ref{fig:map}.}
{\small 
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} lllllrcr}
\hline\hline\vspace*{0.4ex}
\input{inputs/samples-table.tex}
\end{tabular*}
}
\rule{3cm}{0.3pt}

@@

To assemble the markers for this reference baseline, we drew upon several different
sources, as detailed in the separate sections below.

\subsubsection*{Conversion of existing SNPtype assays}

A number of SNP markers from earlier discovery efforts \citep{clemento2011discovery} had already 
been validated as useful for GSI
and PBT in California \citep{clemento2014evaluation}. These markers were originally assayed
using TaqMan (Life Technologies Corp., Carlsbad, CA) probes or SNPtype assays (CITE).
In order to type these markers using amplicon sequencing, we\ldots

\subsubsection*{Additional microhaplotype discovery}

We undertook a new discovery process to develop additional multiallelic
microhaplotype \citep{baetscher2018microhaplotypes} markers in California Chinook.
NEED TO DESCRIBE.

\subsubsection*{Markers around the RoSA region of \citet{thompson2020complex}}

We include amplicons targeting SNPs within the ``Region of Strongest Assocation'' (RoSA)
between spring-run and fall-run fish described in \citet{thompson2020complex}.

Need more here.

\subsubsection*{Identifying and Designing markers from the Late-Fall Associated Region}

To identify loci with large allele frequency differences between late-fall and fall-run Chinook salmon, 
we first conducted a simple case-control GWAS using the low-coverage whole genome sequencing 
data of \citet{thompson2020complex}.  We conducted two separate association-study comparisons.  
The first involved the 16 late-fall run fish as cases with 16 fall-run fish from the Feather River Hatchery as controls. 
The second involved the same 16 late-fall fish as cases, but used 16 fall-run fish from the San 
Joaquin River as controls.  The association studies were performed for each chromosome with 
ANGSD \citep{pmid21663684,korneliussen_angsd_2014}, using the following command: {\footnotesize\tt angsd -yBin \{ybin\}  -r \{chrom\} 
-minMapQ 30 -minQ 20 -minInd 12 -doAsso 1 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP\_pval 1e-6  
-out \{prefix\}  -bam \{bamlist\}}, where {\tt \{ybin\} } is the path to a file indicating the cases and 
controls, 
{\tt \{chrom\} } indicates the chromosome name, {\tt \{prefix\} } is the prefix to use for output files, and 
{\tt \{bamlist\} } is the path to the text file holding paths to the BAM files, one for each individual, ordered as in {\tt \{ybin\} }.

There was only one peak in association scores that was shared between both comparisons (see 
Results). From this peak we identified candidates for followup genotyping by including the 10 
SNPs with the lowest association p-values, and supplementing those with additional SNPs that 
showed:
\begin{itemize}
\item An estimated absolute allele frequency difference (between late-fall and all 32 fall-run fish)  $>0.75$,  with an approximate lower confidence interval of that figure of 0.5,  or
\item An estimated absolute frequency difference of >0.5 with a lower confidence interval >0.25 and 
with either fall-run or late-fall run being nearly fixed for one of the alleles, or
\item An annotation from snpEff \citep{cingolani2012program} of “HIGH” or “MODERATE”, or
\item An absolute frequency difference $>0.48$ and a lower confidence interval of $>0.25$ and a 
genomic  coordinate $> 2.2$~Mb.
\end{itemize}
The final condition was implemented to gather several SNPs within the flanking region to the right of 
the main peak of association.

For the candidate markers found by the above process, we designed amplification primers using 
Primer3 \citep{koressaar2007enhancements,untergasser2012primer3} and tested amplification in a 
subset of Chinook salmon 
samples. The primer pairs that amplified sequence that reliably mapped back to the association- 
peak region were then typed
in a separate collection of 1,638 Sacramento River Chinook salmon sampled from the fish trap below Keswick Dam, including 1,169 winter run, 281 spring 
run, and 188 fall/late-fall run. We divided the fish identified as fall/late-fall via the 125-locus genetic 
stock identification data set into fall run and late fall run according to their sampling date at Keswick: 
99 fish arriving before Dec 26 were classified as fall run and 89 fish arriving after Dec 26 were 
classified as late-fall run.   The allele frequencies of the target SNPs at the remaining amplicons 
were 
estimated for each of these four groups: winter, spring, fall, and late-fall, and we retained
amplicons showing large allele frequency  differences between late-fall fish and all other runs.

\section*{Results}

\subsubsection*{Late-fall Associated Region Markers}

The case-control association test revealed a single peak on chromosome 34 with large allele frequency differences
between Central Valley late-fall and fall-run fish.  This peak was evident both in the comparison of
late-fall fish to fall-run fish in the Feather River Hatchery and of late-fall fish to the fall-run fish in
the San Joaquin River (Fig.~\ref{fig:lfar-assoc}).
%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\newcommand{\lfarcap}{\footnotesize Negative log base 10 of association $p$-values for
individual SNPs for late-fall versus fall run.  $x$ axis shows position in genome (in megabases),
with color alternating by chromosome, as indicated by numbers above the $x$-axis. ``Unk'' refers
to unplaced scaffolds in the Otsh\_v1.0 genome assembly \citep{christensen2018chinook}. The 
upper panel is the comparison between late-fall and Feather River Hatchery fall, while the lower 
panel is the comparison of late-fall to San Joaquin River fall. }
\includegraphics[width=\textwidth]{images/lfar-assoc-faceted.jpg}
\caption[\lfarcap]{\lfarcap}
\label{fig:lfar-assoc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%
The Manhattan plot of Fig.~\ref{fig:lfar-assoc} shows sporadic SNPs with low association
$p$-values.  These are not shared between the two different late-fall to fall comparisons, and
sites that we investigated were concentrated in areas of poor mapping suggesting that their
$p$-values were artifactual.  By contrast, a large number of sites near the prominent peak on
chromosome 34 had large allele frequency differences between late-fall and fall run.  Taking the
top 10 most associated SNPs, and including additional ones from the filtering criteria given in the
Methods, yielded 49 candidate markers for which we designed primers for amplication.  Only 8
of these 49 primer pairs yielded reliable amplification and mapping.   Of these 8, two of the SNPs 
showed inconsistent genotyping and were removed from consideration.  Of the remaining 6, only 3 
showed marked allele frequency differences ($> 0.7$) between late-fall and fall run.  These three 
SNPs (Chr34:828,768,  Chr34:865,057, and Chr34:1,063,084) also had pronounced differences in 
allele frequency between 
late-fall and spring or winter run.

Analysis of the mapping of amplicons for Chr34:828,768 
showed that many ($\approx$89\%) of the reads were off-target (aligning to other chromosomes, 
etc.), making it costly (in terms of sequencing effort) to include the marker in the baseline panel. 
Consequently it was dropped.  The frequency of the different alleles at the two remaining loci
within different reporting units in the baseline are shown in Table~\ref{tab:lfar-freqs}.
%%%%%%%%%%%%%%
\begin{table}
\caption{\footnotesize Allele frequencies across reporting units of the two late-fall associated
markers.  Frequencies are given for the alleles most common amongst late-fall Chinook: nucleotide 
{\tt G} at locus Chr34:865,057 and {\tt A} at Chr34:1,063,084.  $N$ is the total number of gene 
copies available for estimating the allele frequency.}
\label{tab:lfar-freqs}
{\small
\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} lrrrr}
\hline\hline
& \multicolumn{2}{c}{\underline{Chr34:865,057}} & \multicolumn{2}{c}{\underline{Chr34:1,063,084}} \\
Reporting Unit & freq. & $N$ & freq. & $N$ \\ \hline
\input{inputs/lfar-freqs.tex}
\end{tabular*}
}
\vspace*{-2.3ex}\hrule\vspace*{0.3ex}\hrule
\end{table}
%%%%%%%%%%%%%%%
\subsection*{Genetic Variation}

@@

\begin{figure}
\newcommand{\examplecap}{\footnotesize Self-assignment rates  ({\bf a)} and pairwise 
$F_\mathrm{ST}$ values ({\bf b)} for the collections in the baseline.  The codes of the populations
appear on the outer margins of the table atop cells colored according to the run-timing group
of the collection.  Interior cells in which the column and row correspond to the same reporting
unit are colored according to the reporting unit.  For self-assignment tallies, the row corresponds
to the true source collection and the column corresponds to the assigned collection. For $F_\mathrm{ST}$ values, the upper triangle was computed using the baseline microhaplotype
data and the lower triangle was calculated with the whole genome sequence data (where available) 
from \citet{thompson2020complex}.  NOTE: I THINK WE SHOULD MAKE THE LOWER 
DIAGONAL THE P-VALUE FROM A TEST OF DIFFERENTIATION OR SOMETHING LIKE THAT.}
\begin{center}
\includegraphics[width=\columnwidth]{images/gsi_and_fst_fig-crop.pdf}
\end{center}
\caption[\examplecap]{\examplecap}
\label{fig:example}
\end{figure}

### 2024-01-08 tex/data-accessibility.tex
Lots more refinement and additions

{\sc WGSassign} is available as a Python package with these associated links:
\begin{itemize}
\item Development version and entire revision history on GitHub: \url{https://anonymous.4open.science/r/WGSassign-7155}
\item Zenodo archive of initial package release: UPDATE AFTER ANONYMOUS REVIEW
\item Online version of data and scripts used in paper: \url{https://anonymous.4open.science/r/WGSassign-manuscript-data-3072}
\item Data repository with full datasets used in paper. UPDATED WHEN JOURNAL PROVIDES DOI. \url{https://dryad.something.or.other}
\end{itemize}
\mbox{}

>>>>

All data and code needed to reproduce the results here are available online.
\begin{itemize}
\item Online version of data and scripts used in paper: \url{https://github.com/eriqande/california-chinook-microhaps}
\item Archived version of data and scripts used in paper: \url{zenodo link when made}.
\item Data repository with full baseline data set. UPDATED WHEN JOURNAL PROVIDES DOI. \url{https://dryad.something.or.other}
\end{itemize}
\mbox{}
